---
title: "Different extension system typologies promote climate-smart agriculture in West Africa"
subtitle: "Supplementary Material"
author: ''
date: "Last updated: `r Sys.time()`"
output: 
 bookdown::pdf_document2:
    keep_tex: true
    template: helper_utilities/my_templet.tex
    #highlight: zenburn
header-includes:
   - \usepackage[margin=2.8cm]{geometry}
   - \renewcommand{\contentsname}{Table of Contents}
   - \usepackage{enumitem}
   - \usepackage{pifont}
   - \renewcommand{\labelitemi}{$\rightarrow$}
   - \usepackage{tocloft}
   - \renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}
   - \usepackage{hyperref}
   - \hypersetup{linkcolor = blue}
   - \usepackage{hanging}
   - \usepackage[T1]{fontenc}
   - \usepackage{graphicx}
   - \usepackage{booktabs,threeparttablex}
   - \usepackage{pdflscape}
   - \usepackage{fvextra}
   - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
   - \usepackage{lmodern}
   - \usepackage{nimbusmono}
   - \renewcommand{\thetable}{SM\arabic{table}}
   - \setlength{\cfttabnumwidth}{1cm}
   - \usepackage{fouriernc}

toc: false
toccolor: 'blue'
mainfont: 'lm'
toc-title: "Table of Contents"
---

```{r setup, include=FALSE, warning=FALSE, comment=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  out.width = "100%"
)

options(width = 100)
# load the required libraries



# load the required libraries
pacman::p_load(
jsonlite,
sjlabelled,
labelled,
dataMaid,
plotly,
wesanderson,
ggthemes,
hrbrthemes,
sjmisc,
expss,
haven,
knitr,
kableExtra,
ggstream,
ggstatsplot,
highcharter,
tidyverse
)
```
\newpage

\newpage
\listoftables
\newpage

```{r, echo=FALSE}
list_of_tables <- list()
file_names <- list.files(here::here("tables"), pattern = "*.txt")

for(i in 1:length(file_names)){
  list_of_tables[[i]] <- readr::read_delim(here::here("tables", file_names[[i]]), delim = "\t", escape_double = FALSE, trim_ws = TRUE, skip = 1,na = "empty" )
}


names(list_of_tables) <- str_replace(file_names, ".txt", "")


change_names <- function(df){
  names(df) <- str_replace(names(df), "_", "-")
  return(df)
}

list_of_tables <- purrr::map(list_of_tables, change_names)

clean_space <- function(df) {
  df %>%
    mutate_all(~ (str_replace_all(., "%", "\\\\%")))%>%
    mutate_all(~(str_replace_all(., "_", "\\\\_")))%>%
    mutate_all(~(str_replace_all(., "#", "\\\\#")))
}

list_of_tables <- purrr::map(list_of_tables, clean_space)


color_significance <- function(df){
  df[-1] <- lapply(
  df[-1], function(x){
    cell_spec(x, background = ifelse(str_count(x, "\\*")==1, "#8C2981", ifelse(str_count(x, "\\*")==2, "#640A80", ifelse(str_count(x, "\\*")==3, "#3C0F70", "white"))),color = ifelse(str_count(x, "\\*")>=1, "White", "black" ),bold = ifelse(str_count(x, "\\*")>=1,T, F ))
  }
)
  
  return(df)
}

bold_significance <- function(df){
  df[-1] <- lapply(
  df[-1], function(x){
    cell_spec(x, bold = ifelse(str_count(x, "\\*")>=1,T, F ))
  }
)
  
  return(df)
}
```



\begin{table}[]
\caption{Descriptive plot: Distribution of extension systems by year}
\label{tab:my-table2}
\resizebox{\textwidth}{!}{%
\begin{tabular}{l}
\begin{minipage}{\textwidth}
      \includegraphics[width=\textwidth]{descriptive_plot_interest_3.png}
    \end{minipage}
\end{tabular}%
}
\end{table}

\clearpage

\begin{table}[]
\caption{Correlation between CSA practises by country}
\label{tab:my-table}
\resizebox{\textwidth}{!}{%
\begin{tabular}{llrrrrrr}
\hline
Variable1      & Variable2          & \multicolumn{1}{l}{Coefficient} & \multicolumn{1}{l}{Robust std. err.} & \multicolumn{1}{l}{Z} & \multicolumn{1}{l}{P \textgreater Z} & \multicolumn{2}{l}{{[}95\% conf. interval{]}} \\ \hline
\multicolumn{8}{l}{\cellcolor[HTML]{DBE8FF}Overall}                                                                                                                                                                         \\ \hline
Crop rotation  & Improved seeds     & -0.049                          & 0.048                                & -1.02                 & 0.31                                 & -0.143                & 0.045                 \\
Crop rotation  & Intercropping      & 0.348                           & 0.104                                & 3.33                  & 0.001                                & 0.143                 & 0.552                 \\
Crop rotation  & Organic fertilizer & 0.168                           & 0.084                                & 1.99                  & 0.046                                & 0.003                 & 0.332                 \\
Improved seeds & Intercropping      & -0.136                          & 0.041                                & -3.33                 & 0.001                                & -0.216                & -0.056                \\
Improved seeds & Organic fertilizer & 0.141                           & 0.079                                & 1.79                  & 0.074                                & -0.014                & 0.296                 \\
Intercropping  & Organic fertilizer & 0.294                           & 0.083                                & 3.55                  & 0                                    & 0.132                 & 0.457                 \\ \hline
\multicolumn{8}{l}{\cellcolor[HTML]{DBE8FF}Ghana}                                                                                                                                                                           \\ \hline
Crop rotation  & Improved seeds     & -0.043                          & 0.08                                 & -0.53                 & 0.595                                & -0.2                  & 0.114                 \\
Crop rotation  & Intercropping      & 0.029                           & 0.213                                & 0.14                  & 0.891                                & -0.389                & 0.447                 \\
Crop rotation  & Organic fertilizer & 0.034                           & 0.098                                & 0.35                  & 0.724                                & -0.157                & 0.226                 \\
Improved seeds & Intercropping      & -0.237                          & 0.044                                & -5.42                 & 0                                    & -0.323                & -0.152                \\
Improved seeds & Organic fertilizer & 0.047                           & 0.09                                 & 0.52                  & 0.604                                & -0.13                 & 0.223                 \\
Intercropping  & Organic fertilizer & 0.138                           & 0.055                                & 2.52                  & 0.012                                & 0.031                 & 0.246                 \\ \hline
\multicolumn{8}{l}{\cellcolor[HTML]{DBE8FF}Mali}                                                                                                                                                                            \\ \hline
Crop rotation  & Improved seeds     & 0.026                           & 0.154                                & 0.17                  & 0.865                                & -0.276                & 0.328                 \\
Crop rotation  & Intercropping      & 0.271                           & 0.119                                & 2.27                  & 0.023                                & 0.037                 & 0.505                 \\
Crop rotation  & Organic fertilizer & 0.494                           & 0.044                                & 11.34                 & 0                                    & 0.409                 & 0.58                  \\
Improved seeds & Intercropping      & -0.045                          & 0.068                                & -0.66                 & 0.506                                & -0.179                & 0.088                 \\
Improved seeds & Organic fertilizer & 0.24                            & 0.064                                & 3.73                  & 0                                    & 0.114                 & 0.366                 \\
Intercropping  & Organic fertilizer & -0.492                          & 0.287                                & -1.72                 & 0.086                                & -1.053                & 0.07                  \\ \hline
\multicolumn{8}{l}{\cellcolor[HTML]{DBE8FF}Nigeria}                                                                                                                                                                         \\ \hline
Crop rotation  & Improved seeds     & -0.07                           & 0.055                                & -1.27                 & 0.204                                & -0.177                & 0.038                 \\
Crop rotation  & Intercropping      & 0.604                           & 0.117                                & 5.18                  & 0                                    & 0.375                 & 0.832                 \\
Crop rotation  & Organic fertilizer & 0.205                           & 0.107                                & 1.92                  & 0.055                                & -0.005                & 0.415                 \\
Improved seeds & Intercropping      & -0.123                          & 0.05                                 & -2.44                 & 0.015                                & -0.221                & -0.024                \\
Improved seeds & Organic fertilizer & 0.141                           & 0.1                                  & 1.41                  & 0.158                                & -0.054                & 0.336                 \\
Intercropping  & Organic fertilizer & 0.369                           & 0.084                                & 4.39                  & 0                                    & 0.204                 & 0.533                 \\ \hline
\end{tabular}%
}
\end{table}

```{r, echo=FALSE, include=FALSE}
print(".")
```
\pagebreak

\clearpage

```{r}

df <- list_of_tables$si_mvp1%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(Variables = LABELS)%>%
  select(-c(starts_with("ata")))%>%
  bold_significance()

df[1,1] <- "Private extension"
df[3,1] <- "Public extension"
df[5,1] <- "Joint Public-private extension"


kableExtra::kbl(df, longtable = T, booktabs = T,linesep = "", escape=F, col.names = c("Variables", "Crop rotation", "Improved seeds",  "Intercropping", "Organic fertilisers"), align="lrrrr", caption = "Access to extension services and CSA - (CRE)")%>%
#kableExtra::landscape()%>%
#add_header_above(c(" ", "(1)" = 2, "(2)" = 2, "(3)" = 2, "(4)" = 2))  %>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  row_spec(45, hline_after = T)%>%
  row_spec(50, hline_after = T)
```

\newpage

```{r}

df <- list_of_tables$si_mvp2%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(Variables = LABELS)%>%
  select(-c(starts_with("ata")))%>%
  bold_significance()

df[1,1] <- "Private extension"
df[3,1] <- "Public extension"
df[5,1] <- "Joint Public-private extension"

kableExtra::kbl(df, longtable = T, booktabs = T, linesep = "", escape=F, col.names = c("Variables", "Crop rotation", "Improved seeds",  "Intercropping", "Organic fertilisers"), align="lrrrr", caption = "Access to extension services and CSA - (CRE) (Ghana)")%>%
#kableExtra::landscape()%>%
#add_header_above(c(" ", "(1)" = 2, "(2)" = 2, "(3)" = 2, "(4)" = 2))  %>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  row_spec(45, hline_after = T)%>%
  row_spec(50, hline_after = T)
```

\newpage



```{r}

df <- list_of_tables$si_mvp3%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(Variables = LABELS)%>%
  select(-c(starts_with("ata")))%>%
  bold_significance()


df[1,1] <- "Private extension"
df[3,1] <- "Public extension"
df[5,1] <- "Joint Public-private extension"

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, linesep = "", col.names = c("Variables", "Crop rotation", "Improved seeds",  "Intercropping", "Organic fertilisers"), align="lrrrr", caption = "Access to extension services and CSA - (CRE) (Mali)")%>%
#kableExtra::landscape()%>%
#add_header_above(c(" ", "(1)" = 2, "(2)" = 2, "(3)" = 2, "(4)" = 2))  %>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  row_spec(45, hline_after = T)%>%
  row_spec(50, hline_after = T)
```

\newpage

```{r}

df <- list_of_tables$si_mvp4%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(Variables = LABELS)%>%
  select(-c(starts_with("ata")))%>%
  bold_significance()


df[1,1] <- "Private extension"
df[3,1] <- "Public extension"
df[5,1] <- "Joint Public-private extension"

kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, linesep = "", col.names = c("Variables", "Crop rotation", "Improved seeds",  "Intercropping", "Organic fertilisers"), align="lrrrr", caption = "Access to extension services and CSA - (CRE) (Nigeria)")%>%
#kableExtra::landscape()%>%
#add_header_above(c(" ", "(1)" = 2, "(2)" = 2, "(3)" = 2, "(4)" = 2))  %>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  row_spec(45, hline_after = T)%>%
  row_spec(50, hline_after = T)
```


\newpage

```{r}

df <- list_of_tables$pesti_9%>%
  mutate(
    LABELS = case_when(
      LABELS=="" ~ VARIABLES,
      TRUE ~ LABELS
    )
  )%>%
  select(-VARIABLES)%>%
  rename(Variables = LABELS)%>%
  bold_significance()%>%
  select(!starts_with("/"))


kableExtra::kbl(df, longtable = T, booktabs = T, escape=F, linesep = "", col.names = c("Variables", "Overall","Ghana","Mali","Nigeria"), align="lrrrr", caption = "Attrition bias check")%>%
#add_header_above(c(" ", "Use" = 2, "Intensity" = 2))  %>%
kable_styling(font_size = 7, latex_options = c("repeat_header"))%>%
  row_spec(26, hline_after = T)
```


